\section{Other Knowledge}

\subsection{Programming}

\hspace{0.4cm}
I have a good knowledge in programming. The languages that I usually use is Python, Ruby, C++, Java and asembler,
even though my studies provide me facility to learn another language. Also, I use xpath and regular expressions.
I have used agile methodology in the academy so as to learn how it works. For example,
\textbf{Scrum}, \textbf{Extreme Programing}, etc.

Also, I have other skills that makes the programmation easier like using version control system, such as  \textbf{SVN}, \textbf{Mercurial} and \textbf{Git}.

Moreover, I have a strong knowledge in the internal structure of a computer with tecnology IA-32 (Intel Arquitecture of 32 bits).

Finally, I usually give importance to a good presentation of my publications, so I recommend and use $\LaTeX$ to do them. An example could be this Currículum Vitae that you are reading.


\subsection{Configuration of Operating Systems}

\hspace{0.4cm}
A lot of subjects in the university learn the functionality of the operating systems, studing each component separately, such as, the Memory Management Unit (MMU), I/O unit, scheduler, etc. and each functionality distributed systems using well-known algorithm. Also, I have experience in programing with threads or multi-process, using IPC (inter-process comunication), locking, 
Cuento con experiencia de programación con threads o multi-procesos, utilizando IPC (inter-process communication), locking, entre otras técnicas para manejar problemas que surgen por usar muchos hilos de ejecucion.

Otra área la cual me interesa mucho y relacionada con redes, es el area de seguridad informática, si bien no tengo
mucha experiencia laboral en esto, fueron conceptos que siempre me llamaron la atención. Finalizando, me gustaría agregar que también soy usuario domestico del sistema operativo Linux distribución Ubuntu desde el 2009.
